### 2022-08-20 paper/Chapters/Chapter05.tex
update paper update dataset

For the training parameters, we set the training pipeline with a batch size of 8, Adam Optimizer (\cite{adam}), learning rate starting at $ 1\times10^{-3} $, it will decrease at epoch 8 with learning decay factor 0.5. The model is trained using PyTorch 1.10.0a0, CUDA 11.4.1, GPU with an NVIDIA GEFORCE RTXA 6000. We stop training when the angular error of the normal map stops decreasing.

@@

The trip-net model uses a triple GCNN architecture with 4 fusions, which is more difficult to train. It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map. When we train this model, we take the GCNN model as the baseline to observe the advantages of the illuminated information with the trip-net architecture.
We also examined the optimal fusion times of the Trip-Net to determine a possible simplification of the model. A set of similar models was trained with the same settings but different fusion times, denoted Trip-Net-F$ x $, where $ x $ denotes the fusion times. We score the fusion times from 1 to 4. For the learning rate, we initially set $ 1e-3 $. This fits the GCNN model well, but leads to a loss explosion in the trip-net. Therefore, we set a learning rate schedule with an additional decay step at epoch 8. The decay factor is $ 0.5$. The batch size is set to 8.

@@

\section{Quantitative Evaluation on 6 Metrics}
We evaluated our models on a synthetic dataset with a resolution of $ 128 by $ 128. 
Based on the metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for the evaluation. Note that the vertex map input is only semi-dense. One of the advantages of the GCNN architecture is that it is robust to noisy input, so all points, including missing points in the input vertex map, are considered in the evaluation. We use $\tilde{\textbf{N}}$ for the estimated normal map, $ \textbf{N} $ for the ground-truth normal map, $ P $ for the \textit{set} of valid points, \textit{ValidNum} for the number of valid points. \textit{abs} is a function to calculate the absolute value of the given values, \textit{median} is a function to calculate the median value of a given \textit{set}.

\paragraph{Average Angle Error Metric (AAE)}
The metric calculates the average absolute angular error for each point between the inferred normal and the ground-truth normal map.
%% https://www.cuemath.com/geometry/angle-between-vectors/
\[ 
AAE = \frac
{1}
{ValidNum} \cdot \sum_{i\in P}  \left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| 
\]

@@

\[ 
MED = 
\text{Median}   \left( \Bigg\{ \left|\arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \right| \text{for}\ i \in P   \Bigg\}\right)
\]

\paragraph{5 Degree Error Metric ($ E_5 $)}
The metric calculates the percentage of predicted normals that have an error less than $ 5^\circ $ compared to ground truth. First, the number of normals that have an error less than $ 5^\circ $ ($ D_5 $) is calculated.
\[
D_5 = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 5 \right)
\]
Then the percentage of normals that have error less than $ 5^\circ $ ($ E_5 $) is calculated.
\[ 
E_5 = \frac{D_5}{ValidNum}\times 100\%
\]

@@

\[
D_{11.5} = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 11.5 \right)
\]
Then the percentage of normals that have error less than $ 11.5^\circ $ ($ E_{11.5} $) is calculated.
\[ 
E_{11.5} = \frac{D_{11.5}}{ValidNum}\times 100\%
\]

@@

\[
D_{22.5} = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 22.5 \right)
\]
Then the percentage of normals that have error less than $ 22.5^\circ $ ($ E_{22.5} $) is calculated.
\[ 
E_{22.5} = \frac{D_{22.5}}{ValidNum}\times 100\%
\]

@@

\[
D_{30} = \sum_{i\in P} \left( \text{abs}\left(   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right) < 30 \right)
\]
Then the percentage of normals that have error less than $ 30^\circ $ ($ E_{30} $) is calculated.
\[ 
E_{30} = \frac{D_{30}}{ValidNum}\times 100\%
\]

We evaluated our trained models on \textit{synthetic-50-5}. In the test dataset, 5 objects are considered. They are: \textit{Baoshanlu}, \textit{Bus}, \textit{Dragon}, \textit{Garfield} and \textit{Washington}. Each object has 20 scenes with a total of 100 scenes for 5 objects. The test objects are not present in the training dataset. We evaluate all the presented models on the test dataset, to fit them into a table, the names of each model are simplified. The model \textit{SVD} uses the SVD optimization method, the model \textit{NOC} is the no-skip connection version of \textit{GCNN}, \textit{CNN} is the CNN version of \textit{GCNN}. \textit{F1}, \textit{F2}, \textit{F3}, \textit{F4} are the fusion times in the \textit{Trip-Net}.

@@

From the table we can see that all the learning based approaches achieves a better result than SVD approach. In the 30 degrees error metric, GCNN based approach achieves 95 \% accuracy whereas Trip-Net is even higher, some of the models like \textit{dragon} achieves 98\%. The best performance is around 90\%, 75 \%, 45 \% in $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degrees error metrics respectively. Another notable result is the close performance of F3 and F4 models, where they achieves a very comparable performance. We also found that during the training, F4 model converges faster than F3, but F3 in the end achieves a similar loss with model F4. However, based on the $ 30^\circ $, $ 22.5^\circ $, $ 11.5^\circ $ metrics, we can still see that F4 model gives a more stable performance with less high error normals. This is reasonable since the last fusion in the original resolution provides more high resolution information to the models.

@@

From the table, it can be seen that all learning-based approaches achieve a better result than the \textit{SVD} approach. In the 30-degree error metric, the GCNN-based approach achieves 95\% accuracy, while Trip-Net is even higher and some models such as \textit{dragon} achieve 98\%. 
The best performance is 90\%, 75\%, 45\% in the $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degree error metric, respectively. Another notable result is the close relationship between the F3 and F4 models, which achieve very comparable performance. We also found that model F4 converges faster than F3 during training, but F3 ends up achieving a similar loss as model F4. However, using the metrics $ 30^\circ $, $ 22.5^\circ $ and $ 11.5^\circ $, we can see that the F4 model has a more stable performance with less high error normals. This is reasonable since the last fusion at the original resolution provides more high-resolution information to the models.

%% mean metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		Baoshanlu  		& 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 &\textbf{ 9.77 }& 9.80 \\ 
		\hline
		Bus 			& 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & \textbf{7.30} & 7.62\\ 
		\hline
		Dragon 			& 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & 8.16 &\textbf{ 7.79} \\
		\hline
		Garfield 		& 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & 9.71 &\textbf{ 9.39} \\
		\hline
		Washington 		& 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & 12.62 &\textbf{ 12.60}\\
		\bottomrule
	\end{tabular}
	\caption{Average angular error of the evaluation dataset. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-mean}
\end{table}

%% median metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		Baoshanlu  		& 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & 7.54 &\textbf{ 7.50} \\ 
		\hline
		Bus 			& 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & \textbf{3.65 }& 4.47 \\ 
		\hline
		Dragon 			& 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & 5.87 &\textbf{ 5.52} \\
		\hline
		Garfield 		& 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & 6.21 & \textbf{6.04 }\\
		\hline
		Washington 		& 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 &\textbf{ 7.03 }& 7.25\\
		\bottomrule
	\end{tabular}
	\caption{Median angular error of the evaluation dataset. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-median}
\end{table}

%% 5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l |l l l l }
		\toprule
		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		Baoshanlu  		& 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 &\textbf{ 0.33 }& 0.32\\ 
		\hline
		Bus 			& 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & \textbf{0.63 }& 0.55 \\ 
		\hline
		Dragon 			& 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & 0.43 &\textbf{ 0.46}\\
		\hline
		Garfield 		& 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & 0.42 & \textbf{0.43}\\
		\hline
		Washington 		& 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & \textbf{0.40 }& 0.37\\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-5d}
\end{table}

%% 11.5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Object}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		Baoshanlu  		& 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 &\textbf{ 0.69 }& \textbf{0.69}\\ 
		\hline
		Bus 			& 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & \textbf{0.83 }&\textbf{ 0.83 }\\ 
		\hline
		Dragon 			& 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & 0.79 & \textbf{0.81}\\
		\hline
		Garfield 		& 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & 0.74 &\textbf{ 0.75}\\
		\hline
		Washington 		& 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & 0.64 & \textbf{0.65}\\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 11.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-11d}
\end{table}

%% 22.5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Object}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		Baoshanlu  		& 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 &\textbf{ 0.92} &\textbf{ 0.92}\\ 
		\hline
		Bus 			& 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & 0.93 & \textbf{0.94}\\ 
		\hline
		Dragon 			& 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & 0.94 & \textbf{0.95}\\
		\hline
		Garfield 		& 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 &\textbf{ 0.91} &\textbf{ 0.91}\\
		\hline
		Washington 		& 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & \textbf{0.83} &\textbf{ 0.83}\\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 22.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-22d}
\end{table}

%% 30 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		Baoshanlu  		& 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 &\textbf{ 0.97 }&\textbf{ 0.97} \\ 
		\hline
		Bus 			& 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & \textbf{0.96} &\textbf{ 0.96} &\textbf{ 0.96 }\\ 
		\hline
		Dragon 			& 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & 0.97 & \textbf{0.98} \\
		\hline
		Garfield 		& 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & 0.94 & \textbf{0.95 }\\
		\hline
		Washington 		& 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & \textbf{0.89} & \textbf{0.89}\\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 30 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-30d}
\end{table}

@@

A qualitative evaluation of the object \textit{Dragon} is shown in figure \ref{fig:gcnn-eval}. As can be seen in the figure, the \textit{GCNN} model achieves an average angular error of 9 degrees for this object. The image shows an overall good performance for the whole object. A more detailed evaluation can be seen in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy is especially good on the smooth surface, such as the body area. In the same case, as shown in Figure \ref{fig:gcnn-eval-multi-model}, the \textit{NOC} model has an overall worse normal than the \textit{GCNN} model in the smooth area. The \textit{CNN} model retains the skip connection and thus yields a sharper result than the \textit{NOC} model, however, the smooth region of the model is still worse overall than the \textit{GCNN} model. In addition, the \textit{CNN} model yields a much brighter error map (implying a higher angular error) in the sharp regions such as the hind leg and the head region of the dragon object. Figure \ref{fig:gcnn-eval-more} shows further evaluation of the \textit{GCNN} model on other objects.
The \textit{GCNN} model gives a good result, but for the \textit{Washington} model there is still a lack of sharpness in the detail areas such as the face and clothing.

>>>>

For the training parameters, we set the training pipeline with a batch size of 8, Adam Optimizer\cite{adam}, learning rate starting at $ 1\times10^{-3} $, it will decrease at epoch 8 with learning decay factor 0.5. The model is trained using PyTorch 1.10.0a0, CUDA 11.4.1, GPU with an NVIDIA A100 Tensor Core GPU. We stop training when the angular error of the normal map stops decreasing.

@@

The trip-net model uses a triple GCNN architecture with 4 fusions, which is more difficult to train. It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map. When we train this model, we take the GCNN model as the baseline to observe the advantages of the illuminated information with the trip-net architecture.
We also examined the optimal fusion times of the Trip-Net to determine a possible simplification of the model. A set of similar models was trained with the same settings but different fusion times, denoted Trip-Net-F$ x $, where $ x $ denotes the fusion times. We score the fusion times from 1 to 4. For the learning rate, we initially set $ 0.001 $. This fits the GCNN model well, but leads to a loss explosion in the trip-net. Therefore, we set a learning rate schedule with an additional decay step at epoch 8. The decay factor is $ 0.5$. The batch size is set to 8.

@@

\section{Quantitative Evaluation on 6 Metrics}
We evaluated our models on a synthetic dataset with a resolution of $ 128 \times $ 128. 
Based on the metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for the evaluation. Note that the vertex map input is only semi-dense. One of the advantages of the GCNN architecture is that it is robust to noisy input, so all points, including missing points in the input vertex map, are considered in the evaluation. We use $\tilde{\textbf{N}}$ for the estimated normal map, $ \textbf{N} $ for the ground-truth normal map, $ P $ for the \textit{set} of valid points, \textit{K} for the number of valid points. \textit{median} is a function to calculate the median value of a given \textit{set}.

\paragraph{Average Angle Error Metric (AAE)}
The metric calculates the average absolute angular error for each point between the inferred normal and the ground-truth normal map.
%% https://www.cuemath.com/geometry/angle-between-vectors/
\[ 
AAE = \frac
{1}
{K} \cdot \sum_{i\in P}  \left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| 
\]

@@

\[ 
MED = 
\text{median}   \left( \Bigg\{ \left|\arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \right| \text{for}\ i \in P   \Bigg\}\right)
\]

\paragraph{5 Degree Error Metric ($ E_5 $)}
The metric calculates the percentage of predicted normals that have an error less than $ 5^\circ $ compared to ground truth. First, the number of normals that have an error less than $ 5^\circ $ ($ D_5 $) is calculated.
\[
D_5 = \sum_{i\in P} \left( \left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| < 5 \right)
\]
Then the percentage of normals that have error less than $ 5^\circ $ ($ E_5 $) is calculated.
\[ 
E_5 = \frac{D_5}{K}\cdot 100\%
\]

@@

\[
D_{11.5} = \sum_{i\in P} \left( \left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| < 11.5 \right)
\]
Then the percentage of normals that have error less than $ 11.5^\circ $ ($ E_{11.5} $) is calculated.
\[ 
E_{11.5} = \frac{D_{11.5}}{K}\cdot 100\%
\]

@@

\[
D_{22.5} = \sum_{i\in P} \left( \left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| < 22.5 \right)
\]
Then the percentage of normals that have error less than $ 22.5^\circ $ ($ E_{22.5} $) is calculated.
\[ 
E_{22.5} = \frac{D_{22.5}}{K}\cdot 100\%
\]

@@

\[
D_{30} = \sum_{i\in P} \left(\left|   \arccos \frac{\textbf{N}_{i}\cdot \tilde{\textbf{N}}_{i}} {| \textbf{N}_{i} |  |\tilde{\textbf{N}}_{i}|  } \cdot  \frac{180}{\pi}   \right| < 30 \right)
\]
Then the percentage of normals that have error less than $ 30^\circ $ ($ E_{30} $) is calculated.
\[ 
E_{30} = \frac{D_{30}}{K}\cdot 100\%
\]

We evaluated our trained models on \textit{synthetic-50-5}. In the test dataset, 5 objects are considered. They are: \textit{Baoshanlu} (BL), \textit{Bus} (BS), \textit{Dragon} (DG), \textit{Garfield} (GF) and \textit{Washington} (WS). Each object has 20 scenes with a total of 100 scenes for 5 objects. The test objects are not present in the training dataset. We evaluate all the presented models on the test dataset, to fit them into a table, the names of each model are simplified. The model \textit{SVD} uses the SVD optimization method, the model \textit{NOC} is the no-skip connection version of \textit{GCNN}, \textit{CNN} is the CNN version of \textit{GCNN}. \textit{F1}, \textit{F2}, \textit{F3}, \textit{F4} are the fusion times in the \textit{Trip-Net}.

@@

From the table we can see that all the learning based approaches achieves a better result than SVD approach. In the 30 degrees error metric, GCNN based approach achieves 95 \% accuracy whereas Trip-Net is even higher, some of the models like \textit{dragon} achieves 98\%. The best performance is around 90\%, 75\%, 45\% in $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degrees error metrics respectively. Another notable result is the close performance of F3 and F4 models, where they achieves a very comparable performance. We also found that during the training, F4 model converges faster than F3, but F3 in the end achieves a similar loss with model F4. However, based on the $ 30^\circ $, $ 22.5^\circ $, $ 11.5^\circ $ metrics, we can still see that F4 model gives a more stable performance with less high error normals. This is reasonable since the last fusion in the original resolution provides more high resolution information to the models.

@@

From the table, it can be seen that all learning-based approaches achieve a better result than the \textit{SVD} approach. In the 30-degree error metric, the GCNN-based approach achieves 93.53\% accuracy in average, while Trip-Net is 94.81\%. Some models such as \textit{dragon} achieve 97.61\%. 
The Trip-Net achieves around 90\%, 75\%, 45\% in the $ 22.5^\circ $, $ 11.5^\circ $ and $ 5^\circ $ degree error metric, respectively. We also found that model F4 converges faster than less fusion models during training. This is reasonable since the last fusion at the original resolution provides more high-resolution information to the models.

%% mean metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 35.66 & 11.08 & 13.13 & 13.71 & 10.14 & 10.66 & 10.66 & \textbf{10.09} \\ 
		\hline
		BS 			& 31.93 & 7.17 & 8.67 & 11.71 & \textbf{6.85} & 7.52 & 7.93 & 7.09 \\ 
		\hline
		DG 			& 39.57 & 10.58 & 15.02 & 14.78 & 10.03 & 10.34 & 8.52 & \textbf{7.58} \\
		\hline
		GF 		& 39.69 & 9.82 & 12.26 & 14.70 & 9.82 & 9.65 & 9.88 &\textbf{9.50} \\
		\hline
		WS 		& 42.83 & 13.46 & 17.60 & 17.92 & 13.42 & 13.15 & 12.81 &\textbf{12.51}\\
		\bottomrule
	\end{tabular}
	\caption{Average angular error of the evaluation dataset. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-mean}
\end{table}

%% median metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 34.06 & 8.74 & 10.29 & 11.36 & \textbf{7.69} & 8.27 & 8.37 & 7.83 \\ 
		\hline
		BS 			& 34.14 & 3.54 & 4.70 & 8.55 & \textbf{3.01} & 4.01 & 4.69 & 3.56 \\ 
		\hline
		DG 			& 36.43 & 7.53 & 10.68 & 11.85 & 6.74 & 7.47 & 6.17 &\textbf{5.18} \\
		\hline
		GF 		& 37.60 & 6.14 & 8.54 & 11.71 & 6.08 & \textbf{5.86} & 6.38 & 5.96\\
		\hline
		WS 		& 36.89 & 7.45 & 11.19 & 12.70 & 7.43 & 7.19 & 7.28 & \textbf{6.93} \\
		\bottomrule
	\end{tabular}
	\caption{Median angular error of the evaluation dataset. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-median}
\end{table}

%% 5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l |l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 0.59\% & 24.75\% & 20.45\% & 15.86\% & \textbf{34.04\%} & 27.93\% & 26.46\% & 29.41\%\\ 
		\hline
		BS 			& 0.36\% & 62.28\% & 52.70\% & 24.30\% & \textbf{65.98\%} & 59.50\% &  52.56\% & 62.08\% \\ 
		\hline
		DG 			& 0.32\% & 31.05\% & 18.02\% & 13.64\% & 36.64\% & 30.20\% & 40.26\% &\textbf{49.04\%}\\
		\hline
		GF 		& 0.38\% & 43.56\% & 29.39\% & 13.78\% & 43.86\% & \textbf{44.85\%} & 40.42\% & 44.09\%\\
		\hline
		WS 		& 0.18\% & 37.25\% & 27.56\% & 14.42\% & 36.15\% & 38.55\% & 37.76\% & \textbf{39.15\%} \\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-5d}
\end{table}

%% 11.5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 3.48\% & 63.27\% & 54.23\% & 49.93\% &  66.76\% & 65.36\% & 65.12\% & \textbf{68.29\%} \\ 
		\hline
		BS 			& 5.19\% & 83.23\% & 79.37\% & 66.58\% & \textbf{83.62\%} & 82.43\% & 82.04\% & 83.15\%\\ 
		\hline
		DG 			& 2.25\% & 69.75\% & 52.93\% & 48.19\% & 72.64\% & 71.07\% & 77.83\% & \textbf{81.52\%}\\
		\hline
		GF 		& 2.50\% & 73.48\% & 63.11\% & 48.81\% & 73.28\% & 74.21\%  & 72.98\% &\textbf{74.48\%}\\
		\hline
		WS 		& 1.95\% & 62.63\% & 50.17\% & 44.74\% & 62.65\% & 63.73\% & 63.88\% & \textbf{65.07\%} \\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 11.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
	\label{tab:eval-11d}
\end{table}

%% 22.5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 18.18\% & 90.02\% & 84.28\% & 83.93\% & 90.68\% & 90.59\% & 90.96\% & \textbf{92.04\%} \\ 
		\hline
		BS 			& 26.26\% & 93.26\% & 91.39\% & 88.58\% & 93.25\% & 93.22\% & 93.26\% & \textbf{93.47\%}\\ 
		\hline
		DG 			& 13.58\% & 90.11\% & 79.72\% & 82.45\% & 90.33\% & 90.99\% & 93.95\% & \textbf{94.78\%}\\
		\hline
		GF 		& 13.02\% & 89.83\% & 86.63\% & 83.47\% & 89.90\% & 90.18\% & 90.46\% &\textbf{90.72\%}\\
		\hline
		WS 		& 14.29\% & 81.03\% & 71.81\% & 73.11\% & 81.13\% & 81.72\% & 82.68\% &\textbf{83.37\%}\\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 22.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
	\label{tab:eval-22d}
\end{table}

%% 30 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 37.22\% & 95.92\% & 92.88\% & 93.20\% & 96.28\% & 96.06\% & 96.51\% &\textbf{96.85\%} \\ 
		\hline
		BS 			& 43.03\% & 95.80\% & 94.38\% & 93.22\% & 95.74\% & 95.76\% & 95.86\% &\textbf{96.00\% }\\ 
		\hline
		DG 			& 29.87\% & 94.69\% & 87.86\% & 90.61\% & 94.61\% & 95.10\% & 97.15\% & \textbf{97.61\%} \\
		\hline
		GF 		& 27.03\% & 93.76\% & 91.94\% & 90.96\% & 93.75\% & 94.04\% & 94.26\% & \textbf{94.29\%}\\
		\hline
		WS 		& 27.67\% & 87.48\% & 80.57\% & 82.72\% & 87.80\% & 87.90\% & 89.02\% & \textbf{89.30\%}\\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 30 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
	\label{tab:eval-30d}
\end{table}

@@

A qualitative evaluation of the object \textit{Dragon} is shown in figure \ref{fig:gcnn-eval}. As can be seen in the figure, the GCNN model achieves an average angular error of 9 degrees for this object. The image shows an overall good performance for the whole object. A more detailed evaluation can be seen in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy is especially good on the smooth surface, such as the body area. In the same case, as shown in Figure \ref{fig:gcnn-eval-multi-model}, the NOC model has an overall worse normal than the GCNN model in the smooth area. The CNN model retains the skip connection and thus yields a sharper result than the NOC model, however, the smooth region of the model is still worse overall than the GCNN model. In addition, the CNN model yields a much brighter error map (implying a higher angular error) in the sharp regions such as the hind leg and the head region of the dragon object. Figure \ref{fig:gcnn-eval-more} shows further evaluation of the GCNN model on other objects.
The GCNN model gives a good result, but for the \textit{Washington} model there is still a lack of sharpness in the detail areas such as the face and clothing.

### 2022-08-20 paper/Chapters/Chapter06.tex
update paper update dataset

The second network is called Trip-Net and is based on the GCNN model. It is designed for illumination-calibrated RGB-D image-based approaches. This model uses the GCNN architecture three times to process vertex map, light map and image separately. We also found that 4 fusions of the 3 pipes in our models is the key point to improve the performance.
Based on our proposed dataset with resolution $ 128\times 128 $, the experiments show that the models trained on illuminated calibrated RGB-D images improve the accuracy by $ 11.1\% $ of the average degree error compared to the geometry information based approach, which provides more sharpness in the normal map.

>>>>

The second network is called Trip-Net and is based on the GCNN model. It is designed for illumination-calibrated RGB-D image-based approaches. This model uses the GCNN architecture three times to process vertex map, light map and image separately. We also found that 4 fusions of the 3 pipes in our models is the key point to improve the performance.
Based on our proposed dataset with resolution $ 128\times 128 $, the experiments show that the models trained on illuminated calibrated RGB-D images improve the accuracy by $ 10.4\% $ of the average degree error compared to the geometry information based approach, which provides more sharpness in the normal map.
